Human Factors Influencing Visual Statistical Inference

### 2015-08-31 sociology_paper.Rnw
table 6
table 3

\begin{table}[htbp]
\centering
\caption{Analysis of variance (ANOVA) table comparing full model, all the demographic factors, with the reduced models, obtained by removing respective factor variable. Gender does not have a significant effect on detection rate, but does on time to respond. All factors significantly affect time to respond.}
\scalebox{.9}{
\begin{tabular}{rlrrrrrr}
  \hline
\multicolumn{2}{c}{Model}  & AIC & BIC & logLik & Chisq & Chi.Df & $p$-value \\ 
  \hline
Proportion Correct &Full & 23822.00 &23943.00 &-11896.00  & &  &  \\ [3pt]
%& \multicolumn{2}{l}{Reduced}  &  &  &  & \\
{Reduced Models}  &- Age & 23835.22 & 23907.93 & -11908.61 & 25.50 & 6 & $<$0.001 \\ 
  &- Country  & 24099.57 & 24204.72 & -12036.78 & 281.85 & 2 & $<$0.001 \\ 
  &- Education  & 23837.48 & 23926.34 & -11907.74 & 23.77 & 4 & $<$0.001 \\ 
  &- Gender  & 23821.88 & 23934.98 & -11896.94 & 2.17 & 1 & 0.140 \\ 
   \hline
   Log Time Taken &Full &  51904.00 &52034.00 & -25936.00 & &  &  \\ [3pt]
%& \multicolumn{2}{l}{Reduced}  &  &  &  & \\
Reduced Models &- Age  & 52435.63 & 52516.41 & -26207.81 & 543.18 & 6 & $<$0.001 \\ 
 &- Country  & 52849.92 & 52963.15 & -26410.96 & 949.47 & 2 & $<$0.001 \\ 
  &- Education  & 52012.68 & 52109.61 & -25994.34 & 116.23 & 4 & $<$0.001 \\ 
  &- Gender  & 51970.57 & 52091.74 & -25970.28 & 68.12 & 1 & $<$0.001 \\ 
\hline
\end{tabular}
}
\label{tbl:anova_factor}
\end{table}

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Sun Aug 30 22:43:05 2015
\begin{table}[ht]
\caption{\label{tbl:anova_factor}}
\centering
\begin{tabular}{rrrrrlrrrr}
  \hline
 & Deviance & $\chi^2$ & df & $p$-value && Deviance & $\chi^2$ & df & $p$-value \\   \hline
Full & 51872.44 & 0.00 & 6.00 & 0.00 &  & 23791.91 & 0.00 & 6.00 & 0.00 \\ 
  Age & 51329.26 & 543.18 & 6.00 & 0.00 &  & 23766.41 & 25.50 & 6.00 & 0.00 \\ 
  Country & 51496.37 & 376.07 & 2.00 & 0.00 &  & 23765.88 & 26.03 & 2.00 & 0.00 \\ 
  Degree & 51756.21 & 116.23 & 4.00 & 0.00 &  & 23768.15 & 23.76 & 4.00 & 0.00 \\ 
  Gender & 51804.32 & 68.12 & 1.00 & 0.00 &  & 23789.74 & 2.17 & 1.00 & 0.14 \\ 
   \hline
\end{tabular}
\end{table}

@@

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Sun Aug 30 11:15:41 2015
\begin{table}[hbtp]
\centering
\caption{\label{tbl:model_result_response}Parameter estimates of models \eqref{eqn:trend_response} fitted to data from three different experiments using detection rate as the response to assess learning trend. Attempt number is fitted as a factor to enable modeling any sort of non-linear learning trend. Only experiment~6 shows some evidence of a learning trend, with detection rate essentially increasing as attempts increase.}
\scalebox{.81}{
\begin{tabular}{rr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}}
\cline{2-5} \cline{7-10} \cline{12-15} 
& \multicolumn{4}{c} {Experiment~5} & &\multicolumn{4}{c} {Experiment~6} && \multicolumn{4}{c} {Experiment~7}\\
\cline{2-5} \cline{7-10} \cline{12-15} 
Effect & Est & 2.5\% & 97.5\% &  & \hspace{1cm} & Est & 2.5\% & 97.5\% &  & \hspace{1cm} & Est & 2.5\% & 97.5\% &  \\ 
\cline{2-5} \cline{7-10} \cline{12-15} 
Fixed \\
$\mu$ & -1.30 & -1.69 & -0.92 & *** &   & -0.22 & -0.51 & 0.07 &  &   & -1.71 & -2.77 & -0.65 & ** \\ [3pt]
  $\alpha_2$ & 0.27 & -0.19 & 0.73 &  &   & 0.26 & -0.06 & 0.58 &  &   & -0.49 & -1.31 & 0.32 &  \\ 
  $\alpha_3$ & -0.18 & -0.65 & 0.29 &  &   & 0.34 & 0.02 & 0.66 & * &   & -0.19 & -1.01 & 0.63 &  \\ 
  $\alpha_4$ & 0.08 & -0.39 & 0.55 &  &   & 0.36 & 0.04 & 0.68 & * &   & -0.47 & -1.28 & 0.35 &  \\ 
  $\alpha_5$ & 0.30 & -0.17 & 0.77 &  &   & 0.37 & 0.05 & 0.70 & * &   & -0.16 & -0.96 & 0.65 &  \\ 
  $\alpha_6$ & 0.04 & -0.44 & 0.53 &  &   & 0.24 & -0.07 & 0.56 &  &   & -0.03 & -0.87 & 0.82 &  \\ 
  $\alpha_7$ & 0.28 & -0.20 & 0.77 &  &   & 0.16 & -0.16 & 0.48 &  &   & 0.02 & -0.81 & 0.84 &  \\ 
  $\alpha_8$ & -0.04 & -0.54 & 0.45 &  &   & 0.34 & 0.02 & 0.66 & * &   & -0.08 & -0.89 & 0.73 &  \\ 
  $\alpha_9$ & -0.20 & -0.69 & 0.30 &  &   & 0.38 & 0.05 & 0.70 & * &   & 0.15 & -0.71 & 1.02 &  \\ 
  $\alpha_{10}$ & 0.51 & 0.03 & 1.00 & * &   & 0.19 & -0.14 & 0.52 &  &   & -0.28 & -1.14 & 0.58 &  \\ 
  Random \\
  $\sigma^2_u$ & \multicolumn{5}{l}{\phantom{-}0.85}  & \multicolumn{5}{l}{\phantom{-}0.90} & 0.76   \\ 
  $\sigma^2_a$ & \multicolumn{5}{l}{\phantom{-}0.02}  & \multicolumn{5}{l}{\phantom{-}0.03} & 0.06   \\ 
  $\sigma^2_l$ & \multicolumn{5}{l}{\phantom{-}1.48}  & \multicolumn{5}{l}{\phantom{-}1.42} & 3.37   \\ 
\cline{2-5} \cline{7-10} \cline{12-15} 
\end{tabular}}
\end{table}

@@

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Sun Aug 30 11:42:08 2015
\begin{table}[bhtp]
\caption{\label{tbl:model_result_time}Parameter estimates of model~\eqref{eqn:trend_time} fitted for log time taken to evaluate a lineup. Both fixed effects parameters of Attempt ($\alpha_1$ and $\alpha$) are highly significant for all three experiments~5,~6 and~7.}
\centering
\scalebox{0.8}{
\begin{tabular}{lr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}}
\cline{2-5} \cline{7-10} \cline{12-15} 
& \multicolumn{4}{c} {Experiment~5} & &\multicolumn{4}{c} {Experiment~6} && \multicolumn{4}{c} {Experiment~7}\\

>>>>

% \begin{table}[htbp]
% \centering
% \caption{Analysis of variance (ANOVA) table comparing full model, all the demographic factors, with the reduced models, obtained by removing respective factor variable. Gender does not have a significant effect on detection rate, but does on time to respond. All factors significantly affect time to respond.}
% \scalebox{.9}{
% \begin{tabular}{rlrrrrrr}
%   \hline
% \multicolumn{2}{c}{Model}  & AIC & BIC & logLik & Chisq & Chi.Df & $p$-value \\ 
%   \hline
% Proportion Correct &Full & 23822.00 &23943.00 &-11896.00  & &  &  \\ [3pt]
% %& \multicolumn{2}{l}{Reduced}  &  &  &  & \\
% {Reduced Models}  &- Age & 23835.22 & 23907.93 & -11908.61 & 25.50 & 6 & $<$0.001 \\ 
%   &- Country  & 24099.57 & 24204.72 & -12036.78 & 281.85 & 2 & $<$0.001 \\ 
%   &- Education  & 23837.48 & 23926.34 & -11907.74 & 23.77 & 4 & $<$0.001 \\ 
%   &- Gender  & 23821.88 & 23934.98 & -11896.94 & 2.17 & 1 & 0.140 \\ 
%    \hline
%    Log Time Taken &Full &  51904.00 &52034.00 & -25936.00 & &  &  \\ [3pt]
% %& \multicolumn{2}{l}{Reduced}  &  &  &  & \\
% Reduced Models &- Age  & 52435.63 & 52516.41 & -26207.81 & 543.18 & 6 & $<$0.001 \\ 
%  &- Country  & 52849.92 & 52963.15 & -26410.96 & 949.47 & 2 & $<$0.001 \\ 
%   &- Education  & 52012.68 & 52109.61 & -25994.34 & 116.23 & 4 & $<$0.001 \\ 
%   &- Gender  & 51970.57 & 52091.74 & -25970.28 & 68.12 & 1 & $<$0.001 \\ 
% \hline
% \end{tabular}
% }
% \label{tbl:anova_factor}
% \end{table}

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Sun Aug 30 22:43:05 2015
\begin{table}[ht]
\caption{\label{tbl:anova_factor}Analysis of variance (ANOVA) table comparing full model, all the demographic factors, with the reduced models, obtained by removing respective factor variable. Gender does not have a significant effect on detection rate, but does on time to respond. All factors significantly affect time to respond.}
\centering
\scalebox{0.9}{
\begin{tabular}{lrrrrlrrrr}
& \multicolumn{4}{c} {Log Time (model~\ref{eqn:demographic_time})} & &\multicolumn{4}{c} {Detection rate (model~\ref{eqn:demographic_response})}  \\
\cline{2-5} \cline{7-10} 
 & Deviance & $\chi^2$ & df & $p$-value && Deviance & $\chi^2$ & df & $p$-value \\ \cline{2-5} \cline{7-10}
Full  & 51872.4 & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} &  & 23792.0 & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
 - Age & 51329.3 & 543.2 & 6 & $<$0.001 & \hspace{0.5cm} & 23766.4 & 26.0 & 6 & $<$0.001 \\ 
 - Country & 51496.4 & 376.1 & 2 & $<$0.001 &  & 23765.9 & 26.0 & 2 & $<$0.001 \\ 
 - Degree & 51756.2 & 116.2 & 4 & $<$0.001 &  & 23768.2 & 23.8 & 4 & $<$0.001 \\ 
 - Gender & 51804.3 & 68.1 & 1 & $<$0.001 &  & 23789.7 & 2.2 & 1 & 0.140 \\ 
\cline{2-5} \cline{7-10}
\end{tabular}}
\end{table}

@@

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Sun Aug 30 11:15:41 2015
\begin{table}[hbtp]
\centering
\caption{\label{tbl:model_result_response}Parameter estimates of models \eqref{eqn:trend_response} fitted to data from three different experiments using detection rate as the response to assess learning trend. Attempt number is fitted as a factor to enable modeling any sort of non-linear learning trend. Only experiment~6 shows some evidence of a learning trend, with detection rate essentially increasing as attempts increase.}
\scalebox{.81}{
\begin{tabular}{rr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}}
\cline{2-5} \cline{7-10} \cline{12-15} 
& \multicolumn{4}{c} {Experiment~5} & &\multicolumn{4}{c} {Experiment~6} && \multicolumn{4}{c} {Experiment~7}\\
\cline{2-5} \cline{7-10} \cline{12-15} 
Effect & Est & 2.5\% & 97.5\% &  & \hspace{1cm} & Est & 2.5\% & 97.5\% &  & \hspace{1cm} & Est & 2.5\% & 97.5\% &  \\ 
\cline{2-5} \cline{7-10} \cline{12-15} 
Fixed \\
$\mu$ & -1.30 & -1.69 & -0.92 & *** &   & -0.22 & -0.51 & 0.07 &  &   & -1.71 & -2.77 & -0.65 & ** \\ [3pt]
  $\alpha_2$ & 0.27 & -0.19 & 0.73 &  &   & 0.26 & -0.06 & 0.58 &  &   & -0.49 & -1.31 & 0.32 &  \\ 
  $\alpha_3$ & -0.18 & -0.65 & 0.29 &  &   & 0.34 & 0.02 & 0.66 & * &   & -0.19 & -1.01 & 0.63 &  \\ 
  $\alpha_4$ & 0.08 & -0.39 & 0.55 &  &   & 0.36 & 0.04 & 0.68 & * &   & -0.47 & -1.28 & 0.35 &  \\ 
  $\alpha_5$ & 0.30 & -0.17 & 0.77 &  &   & 0.37 & 0.05 & 0.70 & * &   & -0.16 & -0.96 & 0.65 &  \\ 
  $\alpha_6$ & 0.04 & -0.44 & 0.53 &  &   & 0.24 & -0.07 & 0.56 &  &   & -0.03 & -0.87 & 0.82 &  \\ 
  $\alpha_7$ & 0.28 & -0.20 & 0.77 &  &   & 0.16 & -0.16 & 0.48 &  &   & 0.02 & -0.81 & 0.84 &  \\ 
  $\alpha_8$ & -0.04 & -0.54 & 0.45 &  &   & 0.34 & 0.02 & 0.66 & * &   & -0.08 & -0.89 & 0.73 &  \\ 
  $\alpha_9$ & -0.20 & -0.69 & 0.30 &  &   & 0.38 & 0.05 & 0.70 & * &   & 0.15 & -0.71 & 1.02 &  \\ 
  $\alpha_{10}$ & 0.51 & 0.03 & 1.00 & * &   & 0.19 & -0.14 & 0.52 &  &   & -0.28 & -1.14 & 0.58 &  \\ 
  Random \\
  $\sigma^2_u$ & \multicolumn{5}{l}{\phantom{-}0.85}  & \multicolumn{5}{l}{\phantom{-}0.90} & 0.76   \\ 
  $\sigma^2_a$ & \multicolumn{5}{l}{\phantom{-}0.02}  & \multicolumn{5}{l}{\phantom{-}0.03} & 0.06   \\ 
  $\sigma^2_l$ & \multicolumn{5}{l}{\phantom{-}1.48}  & \multicolumn{5}{l}{\phantom{-}1.42} & 3.37   \\ \cline{2-5} \cline{7-10} \cline{12-15} 
\\
\hline
\multicolumn{10}{l}{Signif. codes:  *** $<$ 0.001 $\le$ ** $<$ 0.01 $\le$ * $<$ 0.05 $\le$ . $<$ 0.1 $\le$ ` ' $<$ 1}
\end{tabular}}
\end{table}

@@

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Sun Aug 30 11:42:08 2015
\begin{table}[bhtp]
\caption{\label{tbl:model_result_time}Parameter estimates of model~\eqref{eqn:trend_time} fitted for log time taken to evaluate a lineup. Both fixed effects parameters of Attempt ($\alpha_1$ and $\alpha$) are highly significant for all three experiments~5,~6 and~7.}
\centering
\scalebox{0.9}{
\begin{tabular}{lr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}}
\cline{2-5} \cline{7-10} \cline{12-15} 
& \multicolumn{4}{c} {Experiment~5} & &\multicolumn{4}{c} {Experiment~6} && \multicolumn{4}{c} {Experiment~7}\\
